Incentivizing Exploration with Unbiased History

### 2018-10-17 2level.tex
Respond to Steven's comments

  For each arm $a$, define $q_a$ to be the expected number of arm $a$
  pulls in one run of \ALGG used in the first level.\swcomment{$q_a$
    probability or number?? the issue propagates downwards} By Lemma
  \ref{lem:greedy}, we know $\GdP \leq q_a \leq
  \GdT$.\swcomment{$p_G T$?} Define $W_1^a$ to be the event that the
  number of arm $a$ pulls in the first level is at least
  $q_a T_1- \GdT \sqrt{T_1\log(T)} \geq q_a T_1 / 2$.\swcomment{what
    is the condition on $T_1$ and $T_G$ for this to hold?} By Chernoff
  bound,
\[
\Pr[W_1^a] \geq 1-\exp(-2\log(T)) \geq 1-1/T^2.
\]
Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a}W_1^a$). By union bound, we have
\[
\Pr[W_1] \geq 1- \frac{K}{T^2} \geq 1 - \frac{1}{T}.
\]
\item  \textbf{Concentration of the empirical mean of arm $a$ pulls in the first level:}

>>>>

  For each arm $a$, define $q_a$ to be the expected number of arm $a$
  pulls in one run of \ALGG used in the first level.\swcomment{$q_a$
    probability or number?? the issue propagates downwards} 
    \jmcomment{$q_a$ is the expected number.}
    By Lemma
  \ref{lem:greedy}, we know $\GdP \leq q_a \leq
  \GdT$.\swcomment{$p_G T$?}
  \jmcomment{$q_a$ is only for one run of greedy. Not $T_1$ runs of greedy.}
   Define $W_1^a$ to be the event that the
  number of arm $a$ pulls in the first level is at least
  $q_a T_1- \GdT \sqrt{T_1\log(T)} \geq q_a T_1 / 2$.\swcomment{what
    is the condition on $T_1$ and $T_G$ for this to hold?} 
    \jmcomment{$\GdT$ is a constant. This holds if $T_1 = \omega(\log(T))$ and $T$ is a larger than some constant.}
    By Chernoff
  bound,
\[
\Pr[W_1^a] \geq 1-\exp(-2\log(T)) \geq 1-1/T^2.
\]
Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a}W_1^a$). By union bound, we have
\[
\Pr[W_1] \geq 1- \frac{K}{T^2} \geq 1 - \frac{1}{T}.
\]
\item  \textbf{Concentration of the empirical mean of arm $a$ pulls in the first level:}

### 2018-10-17 model.tex
Respond to Steven's comments

We study the mult-armed bandit problem in a social learning context,
in which a principal faces a sequence of $T$ myopic agents. There is a
set $\A$ of $K$ arms, and the reward from pulling an arm $a\in \A$ is
distributed according to the Bernoulli distribution with an unknown
mean $\mu_a$.\swcomment{do we plan to generalize to real-valued?}  At
each round $t\in [T]$, a new agent $t$ arrives, receives a message
$m_t$ from the principal, chooses an arm $a_t\in \A$, and collects a
reward $r_t\in \{0,1\}$ that is immediately observed by the
principal. Given any sequence of arms $\{a_1, \ldots, a_T\}$ chosen by
the agents, the \emph{regret} is defined as
\[
  \reg(T)= \reg(a_1, \ldots , a_T) = T \max_{a\in \A} \mu_a -
  \sum_{t=1}^T \mu_{a_t}.
\]

@@

\begin{assumption}
\label{ass:embehave}
Let $c_m = 1/16$.\swcomment{subscript $m$ meant anything?}. 
\begin{itemize}
\item The mean reward $\mu_a$ for each arm $a\in \A$ lies in the range
  of $[1/3, 2/3]$.

@@

We allow different agents to have different behavior models as long as
they satisfy Assumption \ref{ass:embehave}. More specifically, we
assume each agent's behavior model is sampled from an unknown
distribution independently.\swcomment{why independently? can be be
  adversarial?}
\begin{remark}
  how this relates to Bayesian exploration with conjugate
  priors\swcomment{seems to be something nasty}
\end{remark}

>>>>

We study the mult-armed bandit problem in a social learning context,
in which a principal faces a sequence of $T$ myopic agents. There is a
set $\A$ of $K$ arms, and the reward from pulling an arm $a\in \A$ is
distributed according to the Bernoulli distribution with an unknown
mean $\mu_a$.\swcomment{do we plan to generalize to real-valued?}  
\jmcomment{Probably not. We probably need some weird assumptions to make it work and we may need to change many parts of our proofs. The assumptions will be like: enough variance for anti-concentration and even more stuff for the greedy to has a small chance to work. Probably binary sound more natural and practical. And we should state something like binary should be interpreted as the feedback from the user, i.e. ``like'' or ``dislike''.}
At each round $t\in [T]$, a new agent $t$ arrives, receives a message
$m_t$ from the principal, chooses an arm $a_t\in \A$, and collects a
reward $r_t\in \{0,1\}$ that is immediately observed by the
principal. Given any sequence of arms $\{a_1, \ldots, a_T\}$ chosen by
the agents, the \emph{regret} is defined as
\[
  \reg(T)= \reg(a_1, \ldots , a_T) = T \max_{a\in \A} \mu_a -
  \sum_{t=1}^T \mu_{a_t}.
\]

@@

\begin{assumption}
\label{ass:embehave}
Let $c_m = 1/16$.\swcomment{subscript $m$ meant anything?} \jmcomment{It means a constant for some assumptions about means but nothing else. Just want to make it different from other constants. Maybe there are better notations.}. 
\begin{itemize}
\item The mean reward $\mu_a$ for each arm $a\in \A$ lies in the range
  of $[1/3, 2/3]$.

@@

We allow different agents to have different behavior models as long as
they satisfy Assumption \ref{ass:embehave}. More specifically, we
assume each agent's behavior model is sampled from an unknown
distribution independently.\swcomment{why independently? can be be
  adversarial?} \jmcomment{Actually current proofs don't work when it's adversarial. It's fairly annoying for the anti-concentration argument. In the proof, we need to use independent to show that the amount of agents pulling arm $a$ in the first level is concentrated to $T_1 q_a$.}
\begin{remark}
  how this relates to Bayesian exploration with conjugate
  priors\swcomment{seems to be something nasty}
\end{remark}
